Annotation exploration for SCPCP000006, `predicted.score` threshold `r params$predicted.score_thr`

### 2024-11-15 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
typo

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )

      # The file may not be present if this is being run in CI, so check first
      # We should error out if the file does not exist and we are NOT testing
      if (!file.exists(input_file) & !params$testing) {
        stop("input RDS file not found.")
      }

>>>>

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_id |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )

      # The file may not be present if this is being run in CI, which is ok.
      # If we are not running in CI and the file doesn't exist, we should error out
      # We should error out if the file does not exist and we are NOT testing
      if (!file.exists(input_file)) {
        if (params$testing) {
          return(NULL)
        } else {
          stop("Input RDS file does not exist.")
        }
      }
